
%---------------------------------------------------
\subsection{Purpose}
The purpose of this document is describing the development of our prototype of SafeStreets, the choices we made in the development , the software we used for developing and for testing and at the end of the document we present how to install and run the developed software.

%---------------------------------------------------
\subsection{Scope}
\subsubsection{Description of the given problem}
SafeStreets is a crowd-sourced application whose intention is to notify the authorities when traffic
violations occur. Citizens, thanks to the system, will be able to send information about violations to the
authorities who will take actions against them. In this way, the service provided by the authorities can be
improved because they will receive notifications through the app. The sources of notifications are the
Citizens who take photos of violations and send them to the authorities through
the application. The information provided by users are integrated with other suitable information and are
stored by the service. The system also runs an algorithm to read the license plate of the vehicle in the
photos. All collected data can be seen by Citizens and authorities to find which streets are the safest.
Users can have different levels of visibility: authorities must be able to know the license plates of vehicles
in the photos, while normal users can only see data in the form of statistics. Moreover, data are sent to the municipal district so that important information can be extracted, and the system makes statistics and suggestion in order to make decisions to improve the safety of the area. Finally, the system will have to be easy to use, reliable
and highly scalable to fit perfectly with the mutable context in which it will be used.



\subsection{Document Structure}
This chapter debates about contents and structure of Implementation and Testing Documnet, indeed this document is divided in  different sections:
\begin{enumerate}
\item	Introduction: This chapter rovides a general definition of the developed software; 
\item Requirements and Functions: This chapter illustrates the requirements which the software meets and the functions developed to satisfy them;
\item Development Choices: This chapter shows the choices made during the developement, the used frameworks, programming languages and softwares are described here.
\item  Structure of the source code:This chapter explains how the source codes are organized.
\item  Testing: This chapter explains how the testing was carried on during the developement.
\item  Installation Instructions : This chapter shows how the software can be installed and run.
\end{enumerate}
